Action alternatives & disruption factor

### 2023-08-25 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/action_alternatives_confidence_factor.Rmd
update aa

# SELF-REPORT DATA
df_sri <- 
  excel_sheets("data/coding_sri.xlsx") %>% 
  map_df(~read_xlsx("data/coding_sri.xlsx",.)) %>% 
  dplyr::select(ID, event, disruption_factor) %>% 
  filter(!ID %in% c(141,
                    142,
                    204,
                    226), # filter relevant rows
         event %in% c("chatting")) %>%
  janitor::clean_names()

@@

# ACTION ALTERNATIVES non-disruptive 
df_alternatives_nd <- read_excel("data/coding_action_alternatives.xlsx") %>% 
  na.locf() %>% 
  janitor::clean_names() %>% 
  select(id, code) %>% 
  mutate(nd = 
           as.numeric(
             case_when(code > 3 ~ '0',
                       code <= 3 ~ '1',
                       TRUE ~ 'F'
                       )
             )
         ) %>%
  group_by(id) %>% 
  summarise(nd = sum(nd))

@@

# creating new column with total reactions
main_novice <- main %>%
  filter(id %in% c("Novice")) %>% 
  mutate(
    # reaction_sum = sum(reaction),
         nd_sum = sum(nd),
         sum_participants = sum(n()),
    # percent_reaction = round((reaction_sum/sum_participants),digits = 2),
         percent_nd = round((nd/count),
                            digits = 2)
         )

# creating new column with total reactions
main_expert <- main %>%
  filter(id %in% c("Expert")) %>% 
  mutate(
    # reaction_sum = sum(reaction),
         nd_sum = sum(nd),
         sum_participants = sum(n()),
    # percent_reaction = round((reaction_sum/sum_participants), digits = 2),
         percent_nd = round((nd/count),
                            digits = 2)
         )

@@

@@

# action alternatives - count
describeBy(main$count, main$id)
plot_action_count <- boxplot(count ~ id, data = main)^

# action alternatives - non disruptive alternatives (sum score)
describeBy(main$nd, main$id)
plot_action_quality <- boxplot(nd ~ id, data = main)

@@

@@

#### disruption factor
# t-test for expertise differences
t.test(x = main$disruption_factor[main$id == "Expert"],
       y = main$disruption_factor[main$id == "Novice"])

@@

### action alternatives count
# t-test for expertise differences
t.test(x = main$count[main$id == "Expert"],
       y = main$count[main$id == "Novice"])

@@

### action alternatives non-disruptive absolute score
# t-test for expertise differences
t.test(x = main$nd[main$id == "Expert"],
       y = main$nd[main$id == "Novice"])

@@

### action alternatives non-disruptive relative score
# t-test for expertise differences
t.test(x = main$percent_nd[main$id == "Expert"],
       y = main$percent_nd[main$id == "Novice"])

>>>>

# SELF-REPORT DATA
df_sri <- 
  excel_sheets("data/coding_sri.xlsx") %>% 
  map_df(~read_xlsx("data/coding_sri.xlsx",.)) %>% 
  dplyr::select(ID, event, disruption_factor, confidence_factor) %>% 
  filter(!ID %in% c(141,
                    142,
                    204,
                    226), # filter relevant rows
         event %in% c("chatting")) %>%
  janitor::clean_names()

@@

# ACTION ALTERNATIVES non-disruptive 
df_alternatives_nd <- read_excel("data/coding_action_alternatives.xlsx") %>% 
  na.locf() %>% 
  janitor::clean_names() %>% 
  select(id, code) %>% 
  mutate(nd = as.numeric(case_when(code > 3 ~ '0',
                                   code <= 3 ~ '1',
                                   TRUE ~ 'F'
                                   )
                         )
         ) %>% 
  select(id, nd) %>% 
  group_by(id) %>%
  summarise(nd = sum(nd))

@@

# creating new column with absolute number of nd-alternatives
main_novice <- main %>%
  filter(id %in% c("Novice")) %>% 
  mutate(percent_nd = round((nd/count),
                            digits = 2)
         )

# creating new column with absolute number of nd-alternatives
main_expert <- main %>%
  filter(id %in% c("Expert")) %>% 
  mutate(percent_nd = round((nd/count),
                            digits = 2)
         )

@@

# confidence factor
describeBy(main$confidence_factor, main$id)
plot_disrup <- boxplot(confidence_factor ~ id, data = main)

@@

# action alternatives - count
describeBy(main$count, main$id)
plot_action_count <- boxplot(count ~ id, data = main)

# action alternatives - non disruptive alternatives (absolute score)
describeBy(main$nd, main$id)
plot_action_quality <- boxplot(nd ~ id, data = main)

@@

# 
main %>% 
  group_by(id) %>% 
  summarise(disruption_factor = n(),
            confidence_factor = n(),
            count = n(),
            nd = n(),
            percent_nd = n())

table(main$disruption_factor)
table(main$confidence_factor)
table(main$count)
table(main$nd)
table(main$percent_nd)

@@

#### disruption factor
# t-test for expertise differences
t.test(x = main$disruption_factor[main$id == "Expert"],
       y = main$disruption_factor[main$id == "Novice"],
       var.equal = TRUE)

@@

#### confidence factor
# t-test for expertise differences
t.test(x = main$confidence_factor[main$id == "Expert"],
       y = main$confidence_factor[main$id == "Novice"],
       var.equal = TRUE)

# effect size for expertise differences
CohenD(x = main$confidence_factor[main$id == "Expert"],
       y = main$confidence_factor[main$id == "Novice"],
       na.rm = TRUE)

### action alternatives count
# t-test for expertise differences
t.test(x = main$count[main$id == "Expert"],
       y = main$count[main$id == "Novice"],
       var.equal = TRUE)

@@

### action alternatives non-disruptive absolute score
# t-test for expertise differences
t.test(x = main$nd[main$id == "Expert"],
       y = main$nd[main$id == "Novice"],
       var.equal = TRUE)

@@

### action alternatives non-disruptive relative score
# t-test for expertise differences
t.test(x = main$percent_nd[main$id == "Expert"],
       y = main$percent_nd[main$id == "Novice"],
       var.equal = TRUE)
